Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-21 analysis/paper/supplementary-material.Rmd
delete replicated code chunk
get mcmc diagnostic plots all on one plot

```{r diag-plots}
png(filename = here::here("analysis", "figures", "008-pre-diag.png"),
    width = 10, height = 8, units = "in", res = 360)
plot(pre_bergm)
dev.off()
```

@@

>>>>

```{r diag-plots}
# get the first set of diagnostic plots
x <- pre_bergm

png(filename = here::here("analysis", "figures", "008-pre-diag.png"),
    width = 10, height = 12, units = "in", res = 360)

seqq <- 4
par(mfrow = c(x$dim, 3), 
    oma   = c(0, 0, 3, 0), 
    mar   = c(4, 3, 1.5, 1))

for (i in 1:x$dim) {

  plot(density(x$Theta[, i]), 
       main = "", 
       axes = FALSE, 
       xlab = bquote(paste(theta[.(i)], " (", .(x$specs[i]), ")")),
       ylab = "", lwd = 2)
  axis(1)
  axis(2)
  coda::traceplot(x$Theta[, i], type = "l", xlab = "Iterations", ylab = "")
  coda::autocorr.plot(x$Theta[, i], auto.layout = FALSE)
  if (x$dim > 4) seqq <- seq(4, x$dim, 4)
  if (i %in% union(x$dim, seqq)) {
    title(paste("MCMC output for Model: y ~", x$formula[3]), outer = TRUE)
  }
}

dev.off()
```

@@

```{r xx1, fig.cap = "xx1"}
knitr::include_graphics(here::here("analysis", "figures", "008-pre-diag.png"))
```
